\section{Conclusion}
Monitoring of water quality is nowadays extremely important as it's widely fed by the public. IoT has faced difficulties in the field of traditional water quality tracking and water testing, mostly centred in the period. Similarly, the current water quality tracking for assessment does not contain any intelligence. Now with the arrival of the machine to communicate with other machines which include items to communicate to each other and can be used in large geographical areas in comparison to the small area as seen in the previous device. As a result, a wise water quality monitoring machine based on IoT was advanced right here. This proposed system can solve a large number of problems regarding this topic. The sensor data is sent serially to Arduino UNO, where the Arduino learns the logic used to calculate water quality. Cloud servers have stored the documents and projected results. This has led to IoT technology being used in the automatic water monitoring system, where the sensors can interconnect to measure residential water quality. This shows that there is no human interference to automatically regulate water safety. This device should be implemented not only in the supply tank but also in a river, lake and wetlands. For predicting and future operation the data should be stored carefully.

\pagebreak
\section{Limitation and Future Work}
A cost-effective, real-time monitoring system for water quality has been implemented and tests performed. Here an experimental setup is performed. This system allows administrative staff to monitor the levels of contamination inside water systems. In the future notifications can be sent to every user when the water gets dirty. In this experimental setup, low-cost components are used so an Industrial graded waterproof sensor should be used. The structure can be designed in such a shape that it can be used anywhere. Due to Covid, it was not possible to set this device at the real supply line. If possible then real data would get and use that data machine learning algorithms could be applied. Thus we could predict the water quality at a different place at different time. We did not use individual chemical sensor due to the high price. Again we flushed thee total dirty water. In future, we can make an automated process to refine dirty water. Internet of Things (IoT) and its services are becoming part of our life, ways of running, and business. High-quality studies are being conducted on the development of essential building blocks and modes to support a range of relevant technology network solutions.

\newpage

% \pagebreak
% \begin{landscape}
% \begin{table}[]
% \begin{tabular}{|c|c|c|c|c|}
% \hline
% \textbf{}            & \textbf{Data updated to cloud server}                                       & \textbf{Quality found}                                                        & \textbf{Clean and flush}                                                     & \textbf{Message send with location}                                          \\ \hline
% \textbf{Found right} & \textbf{27}                                                                 & \textbf{28}                                                                   & \textbf{28}                                                                  & \textbf{14}                                                                  \\ \hline
% \textbf{Found wrong} & \textbf{3}                                                                  & \textbf{2}                                                                    & \textbf{2}                                                                   & \textbf{6}                                                                   \\ \hline
% \textbf{Result}      & \textbf{\begin{tabular}[c]{@{}c@{}}27/(27+3) *100   \\ = 90\%\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}28/(28+2) * 100    \\ = 93\%\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}28/(28+2) * 100   \\ = 93\%\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}14/(14+6) * 100   \\ = 70\%\end{tabular}} \\ \hline
% \end{tabular}
% \end{table}
% \end{landscape}

